\addcontentsline{toc}{chapter}{Tài liệu tham khảo}
\begin{thebibliography}{9}
	\bibitem{Ajtai96}M. Ajtai. \textit{Generating hard instances of lattice problems. In Proc. 28th ACM Symp. on Theory of Computing, pages 99–108, 1996. Available from ECCC at http://www.uni-trier.de/eccc/.}
	\bibitem{main} Daniele Micciancio, Oded Regev, \textit{Worst-case to Average-case Reduction based on Gaussian Measures} 
	\bibitem{Peikert1} Chris Peikert, \textit{Latiices in cryptography - Lecture 1 - Mathematical Background}.
	\bibitem{Regev9} Oded Regev, \textit{Lattices in Computer Science - Lecture 9 - Fourier transform}
	\bibitem{MiGo} D. Micciancio and S. Goldwasser, \textit{Complexity of Lattice Problem: A Cryptographic Perspective, volume 671 of The Kluwer International Series in Engineering and Computer Science}. Kluwer Academic Publishers, Boston, Massachusetts, Mar. 2002
	\bibitem{Baibai86} L. Baibai. \textit{On Lovasz' lattice reduction and the nearest lattice point problem. Combinatorica, 6(1):1–13, 1986. Preliminary version in STACS 1985.}
	\bibitem{Mic02} D. Micciancio. \textit{Generalized compact knapsacks, cyclic lattices, and efficient one-way functions from worst-case complexity assumptions. Technical Report TR04-095, ECCC Electronic Colloquium on Computational Complexity, 2004. Preliminary version in FOCS 2002}.
	\bibitem{Ban93}W. Banaszczyk. \textit{New bounds in some transference theorems in the geometry of numbers. Mathematische Annalen, 296(4):625–635, 1993}
	\bibitem{YCai03}J.-Y. Cai. \textit{A new transference theorem in the geometry of numbers and new bounds for Ajtai’s connection factor. Discrete Applied Mathematics, 126(1):9–31, Mar. 2003. Preliminary version in CCC 1999.}
	\bibitem{Regev03} O. Regev. \textit{New lattice-based cryptographic constructions. Journal of the ACM, 51(6):899–942, 2004. Preliminary version in STOC 2003}.
	\bibitem{AhaReg04} D. Aharonov and O. Regev. \textit{Lattice problems in NP intersect coNP. Journal of the ACM, 52(5):749–765, 2005. Preliminary version in FOCS 2004}.
	\bibitem{Mic02-STOC} D. Macciancio. \textit{Almost perfect lattices, the covering radius problem, and applications to Ajtai’s connection factor. SIAM Journal on Computing, 34(1):118–169, 2004. Preliminary version in STOC 2002}.
	\bibitem{HaPham02} Hà Huy Khoái - Phạm Huy Điển. \textit{Số học thuật toán, NXB ĐHQG Hà Nội, 2002}.
\end{thebibliography}